ManuscriptFigures

### 2024-01-18 Code/ManuscriptFigures.Rmd
removed the RPackages.bib in this RMD and placed it in the manuscript RMD
Changed PlotsPath to PlotsOut for clarity

knitr::write_bib(c("tidyverse", "lubridate","knitr", "stringr", "broom", "zoo", "RColorBrewer", "grid", "glue", "bookdown","egg"), 'RPackages.bib')

@@

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..","Data", "CleanData")
PlotsPath <- file.path("..","Output", "Figures")
# DataOut <- file.path("..","GrowthAssessData")

>>>>

@@

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..","Data", "CleanData")
PlotsOut <- file.path("..","Output", "Figures")
# DataOut <- file.path("..","GrowthAssessData")
